### 2020-12-26 latex/vnhcs.tex
Edit of the comparison with existing VNHC literature, plus an addition to the conclusion

>>>>

\section{Comparison with Existing VNHC Literature}\label{ch:vnhc-compare}

Griffin and Grizzle were the first to use the unactuated conjugate of momentum
to define relative degree \(\{2,\ldots,2\}\) VNHCs in
\cite{nhvc_dynamic_walking} and \cite{nhvc_gait_optimization}.
\citet{hybrid_zero_dynamics_bipedal_nhvcs} extended their work by defining
the unactuated coordinate \(q_u = B^\perp q\) and specifying that a
VNHC must use the conjugate of momentum to \(q_u\).
This idea is what inspired us to use Hamiltonian mechanics in simply actuated
coordinates, which are more suitable for the study of VNHCs than
Lagrangian mechanics.

Our definition of a VNHC is more general than that of Griffin and
Grizzle.
They define a VNHC as a relation \(h(q,\sigma_u)\), where \(\sigma_u\) is the
Lagrangian mechanics proxy for \(p_u\).
By contrast, our definition of a VNHC allows for relations \(h(q,p)\)
that use the full phase.
Moreover, we are the first to provide the definition of regular VNHCs, and to
provide the characterization in Theorem \ref{thm:vnhc-regularity}.

\citet{hybrid_zero_dynamics_bipedal_nhvcs} derive the
constrained dynamics for VNHCs of the form \(h(q,\sigma_u)\).
For our derivation of the constrained dynamics in Theorem
\ref{thm:zero-dynamics}, we use the same assumptions as they do, with the
additional assumption that one can solve for \(q_a = f(q_u,p_u)\) on \(\Gamma\).
While this means Horn \etal's constrained dynamics hold for a larger class of VNHCs, 
their derivations are obscured by a need to use more complicated machinery
to find the closed form of the dynamics. 
By making the aforementioned additional assumption, we were able to find a the constrained
dynamics as functions of the unactuated coordinates.
Hence, our constrained dynamics are thus more physically intuitive than those of
Horn \etal~% no period because etal has one 
Finally, the additional structure of our constrained dynamics will allow us to
more easily study energy injection properties of VNHCs in the next two chapters.
